A Streaming Algorithm for 2-Center with Outliers in High Dimensions

### 2015-05-02 paper.tex
Adding more descriptin in finding r last paragraph (case r > l_i)

%When the first non-zero radius is observed, $l_1$ is set. 
We run $m$ instances of Algorithm~\ref{alg:smallc} for each value $r \in R_i$ in parallel. 
%for all the previous points, which have been stored in a buffer. It is not hard to see that the space complexity for storing these points is $\O(z)$. 
Whenever a new point $p_i$ is added, 
if $\ell_i=\ell_{i-1}$, then $R_i = R_{i-1}$,
and the new point is inserted to all parallel instances. %corresponding to candidates in $L_i$. 
%Otherwise, Algorithm~\ref{alg:smallc} should be executed for all of the candidates in $L_i$, with all the points. But this is not achievable due to space limitations. 
If $\ell_i > \ell_{i-1}$, then the set $R_i$ has two types of values.
Those values in $R_i$ which are less than $1.2\ell_i$ are also present in $L_{i-1}$,
because $t_i / t_{i-1}$ is a positive power of 2.
For these values, we continue executing the corresponding instance.
If a value $r \in R_i$ is not present in $R_{i-1}$, 
then we have $r \ge 1.2 \ell_{i - 1} \ge \ell_{i-1}$.
%To overcome this problem, note that if the candidate $x_j=j \times t_i \in L_i$ is also in $L_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued. If $x_j \notin L_{i-1}$, then it is certain that $x_j \ge l_{i - 1}$ (Observe that $l_i=ul_{i-1}$, for some $u\in \mathbb{N}$). 
Since those points not lying in the candidate solution 
are saved in the buffer of Algorithm~\ref{alg:1-center} (which has size at most $z$), 
all non-outlier points of this algorithm lie in the candidate balls of Algorithm~\ref{alg:smallc}. 
These outliers have been stored in a buffer. 
Therefore, for a new value $r$, 
it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points in $B_1$.
%Overall, we get the following result.

>>>>

%When the first non-zero radius is observed, $l_1$ is set. 
We run $m$ instances of Algorithm~\ref{alg:smallc} for each value $r \in R_i$ in parallel. 
%for all the previous points, which have been stored in a buffer. It is not hard to see that the space complexity for storing these points is $\O(z)$. 
Whenever a new point $p_i$ is added, 
if $\ell_i=\ell_{i-1}$, then $R_i = R_{i-1}$,
and the new point is inserted to all parallel instances. %corresponding to candidates in $L_i$. 
%Otherwise, Algorithm~\ref{alg:smallc} should be executed for all of the candidates in $L_i$, with all the points. But this is not achievable due to space limitations. 
If $\ell_i > \ell_{i-1}$, then the set $R_i$ has two types of values.
Those values in $R_i$ which are less than $1.2\ell_i$ are also present in $L_{i-1}$,
because $t_i / t_{i-1}$ is a positive power of 2.
For these values, we continue executing the corresponding instance.
If a value $r \in R_i$ is not present in $R_{i-1}$, 
then we have $r \ge 1.2 \ell_{i - 1} \ge \ell_{i-1}$.
%To overcome this problem, note that if the candidate $x_j=j \times t_i \in L_i$ is also in $L_{i-1}$, there is no need to start Algorithm~\ref{alg:smallc} over and the current execution will be continued. If $x_j \notin L_{i-1}$, then it is certain that $x_j \ge l_{i - 1}$ (Observe that $l_i=ul_{i-1}$, for some $u\in \mathbb{N}$). 
Since those points not lying in the candidate solution 
are saved in the buffer of Algorithm~\ref{alg:1-center} (which has size at most $z$), 
all non-outlier points of this algorithm lie in the candidate balls of Algorithm~\ref{alg:smallc} which has center $p_1$ and radius $l_{i-1}$. 
These outliers have been stored in a buffer. 
Since Algorithm~\ref{alg:smallc} maintains two balls with radius at least $r$, which one of them (say $B_1$) has center $p_1$, then all non-outlier points of Algorithm~\ref{alg:1-center} are in $B_1$ and so they do not make transition in Algorithm~\ref{alg:smallc} states.
Therefore, for a new value $r$, 
it suffices to execute Algorithm~\ref{alg:smallc} with only the outlier points in $B_1$,.
%Overall, we get the following result.
